%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Career Summary}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\vspace*{0.05in}
%---------------------------------------------------------
	\cventry		  
    	{ Drone path planning using RRT and CNN} % Job title
    	{ Graduate Research Assistant, Learning and Adaptive Robotics Laboratory (LEARN)} 
    	{The University of Texas at Arlington}
    	{Jan. 2019 - Present} % Date(s)    
    	{
      		\begin{cvitems} % Description(s) of tasks/responsibilities
        		\item { Due to extraordinary performance during master's thesis, chosen over PhD candidates to research efficient heuristic formulation approaches for drone motion planning based of Convolutional Neural Networks (CNN), Reinforcement Learning (RL) and Rapidly-exploring Random Tree (RRT)} \vspace*{0.05in}
      		\end{cvitems}  
    	}
    	
    	
%-------------------------------------        
	\cventry  
    	{Image Caption Generation using encoder-decoder based 		architectures}
    	{Graduate Researcher (Dr. Manfred Huber)} % Job title
    	{The University of Texas at Arlington} % Location
    	{Sep. 2017 - May 2019} % Date(s)
    	{  
      		\begin{cvitems} % Description(s) of tasks/responsibilities		
				\item {\textbf{Research:} Innovated a State-Of-The-Art captioning system, illustrating significance of context-based architectural design thereby opening up new ways of addressing context and the overall task of image captioning}
				\item {\textbf{Development:} Data Preparation -  cleaning, normalizing and visualizing image and text data (used  torchvision, skimage, scipy, numpy, matplotlib, json, xml and pandas); Data Loading: designing efficient data loader for handling millions of images (utilized thread management and parallel processing); creating neural network based architecture  (used OOP concepts and expertise in encoder (CNN) - decoder (RNN) deep learning pipeline setup); Optimization: writing loss functions and reward functions (Reinforcement Learning); multi-gpu training (pytorch and cuda); and Network Visualization: used tensorboard}		
				\item {\textbf{Inference:} System learns to harmonize two structurally different modalities of image feature-vectors and word-vectors, thereby producing balance in text-based attention and visual attention. This work establishes the highly desired skill of crafting deep neural network architectures aimed at extracting insightful information from data and being able to channelize research into products} 
 				\vspace*{0.05in}
      		\end{cvitems}
		} 
		
		
		
		
		
	\cventry
		{Systematix Technologies Pvt. Ltd.}  	
  		{Contract Software Developer}
		{Bhopal, Madhya Pradesh, India}
		{Feb. 2016 - Jul. 2016}	
		{
			\begin{cvitems} % Description
				\item {Channelized the ability to gain domain knowledge quickly and reflect it into technical systems. Developed efficient modules for accountants} \vspace*{0.05in}
			\end{cvitems}
		}




%---------------------------------------------------------
	\cventry
		{iVolunteer}  	
  		{Contract Software Developer}
		{Bhopal, Madhya Pradesh, India}
		{Oct. 2015 - Apr. 2016}	
		{
			\begin{cvitems} 
				\item {Displayed strong coding and verbal abilities by making amendments to `Prayatna' foundation's  website and introduced new features on it: https://www.prayatnasoe.org}  \vspace*{0.05in}
			\end{cvitems}
		}
		


%---------------------------------------------------------
	\cventry
		{Nagarro Software Pvt. Ltd.}    
    	{Software Engineer} % Job title
    	{Gurgaon, Haryana, India} % Location
    	{Apr. 2014 - Sep. 2015} % Date(s)
    	{
      		\begin{cvitems} % Description(s) of tasks/responsibilities
				\item {One of the 3 students out of nearly 6000 students in the whole off-campus drive comprising of 4 universities to clear first coding round. Cleared 3 more rounds to get selected for an offer. Impressed by my technical and analytical scores in the rounds, Nagarro organized an on-campus hiring drive in my university}
				\item {Completed training in 4 months instead of designated 6 months and got promoted to, “Junior Associate” for handling one of the most significant projects of the company, ``Syntona Finac”}        
        		\item {Displayed technical expertise through fast and  accurate development and made responsible for multiple projects: ``Ecova" and ``Syntona Finac". Worked brilliantly as a team player to simultaneously manage both projects following Agile software development methodology}
        		\item {Received 85\% appraisal at the end of 1\st year of job with a title of the star performer among Junior Associates in Technology}  \vspace*{0.05in}
      		\end{cvitems}
    	}
%------------------------------------------------------



\cventry
		{Bharat Heavy Electricals Limited (B.H.E.L.)}    
    	{Software Engineer Intern} % Job title
    	{Bhopal, M.P., India} % Location
    	{May 2013 - Jul. 2013} % Date(s)
    	{
      		\begin{cvitems} % Description(s) of tasks/responsibilities
				\item {Received an opportunity to build material management interface as an intern at India's largest power generation equipment manufacturer}
				\item {Implemented customized sorting in a .NET grid with minimum postback requests for better performance. The project increased production speed by 60\% resulting from swift material management 
}      %  \vspace*{0.06in}
      		\end{cvitems}
    	}
\end{cventries}
    	
    	
    	